Improving the modelling of tempo and phoneme duration

### 2017-04-05 Paper/Paper_v1.tex
Added some more things to Basics.

\chapter{Basics}
\section{Data Mining}
Data Mining means in foreground looking for patterns in data with the help of computers. Patterns are helpful for humans to understand data. They reduce the amount of data, and of available features to the relevant ones. Computers help process within resonable time amounts of data that would need years of manual processing.

@@

@@

\subsection{REPTree}

\subsection{M5P}
The M5P model tree \cite{Witten2011} is a decision tree based on the M5 algorithm introduced by Quinlan (1992). It builds a usual classification tree out of the attributes, and retrieves a linear regression model in each leaf out of the attributes contained in that specific subtree.

@@

\section{Performance Evaluation}
Models produced by machine learning may have different performance levels, which may be evaluated in several ways. We decided for the following three:
\begin{enumerate}
	\item \textbf{RMSE} or \textbf{root mean squared error} measures the differences between the numeric values predicted by a model and those actually observed: 
$RMSE = \sqrt{\frac{\sum(predicted-actual)^2}{n}}$. It is a very popular method for evaluating errors of a model, but it is very sensible to outliers.
	\item \textbf{MAE} or \textbf{mean absolute error} is similar to RMSE, but penalises outliers less. It is computed using the average of the absolute errors: $MAE = \frac{\sum\left|predicted-actual\right|}{n}$
	\item The \textbf{correlation coefficient} is a number between -1 and 1 that quantifies the correlation between two variables, each having a separate value set. We can interpret this as how much the variable movement through its value set corresponds to the movement of the other variable in its own value set. Values close to 1 mean that greater values of the one variable imply greater values for the second variable, negative values mean the two variables move in opposite directions, and values close to 0 mean there is no correlation between the two variables. However, one must keep in mind that correlation does not imply causality, so the presence of correlation between two variables does not mean that one of them has any influence on the other one. If we compare red Ferrari cars to blue Renault cars, one may find a correlation between car color red and car speed. However, this does not imply that red cars are faster.
\end{enumerate}

\section{Tools}

>>>>

\chapter{Basics}

@@

Data Mining means in foreground looking for patterns in data with the help of computers. Patterns are helpful for humans to understand data. They reduce the amount of data, and of available features to the relevant ones. Computers help process within resonable time amounts of data that would need years of manual processing.

@@

\subsection{Decision trees}
Decision trees divide the attribute space into well defined clusters, identified by a class name or a numeric value. In the first case we are dealing with a classification tree, in the second one with a regression tree. If one needs to combine the two methods, he/she may use a classification and regression tree, called CART, or a model tree. The advantage of trees is that new instances are easily assigned to a class, or a numeric value, or a linear model which leads to such a numeric value, and they are easy to unterstand.

The \textbf{M5P model tree} \cite{Witten2011} is a decision tree based on the M5 algorithm introduced by Quinlan (1992). It builds a usual classification tree out of the attributes, and retrieves a linear regression model in each leaf out of the attributes contained in that specific subtree. Branching is realised based on the reduction of variation within the resulting subset.

A \textbf{REPTree} is a decision and regression tree similar to M5P, but optimized for speed. This means it sorts values for numeric attributes only once.

Both trees

@@

\section{Performance Evaluation}
Models produced by machine learning may have different performance levels, which may be evaluated in several ways. As they assess different features of the models, and treat outliers differently, we didn't want to rely only on one of them. Furthermore, we wanted to be able to compare the results with results presented in the literature. After studying the common evaluation methods used for other phoneme prediction models, we chose the following three: 
\begin{enumerate}
	\item \textbf{RMSE} or \textbf{root mean squared error} measures the differences between the numeric values predicted by a model and those actually observed: 
$RMSE = \sqrt{\frac{\sum(predicted-actual)^2}{n}}$. It is a very popular method for evaluating errors of a model, but it is very sensible to outliers.
	\item \textbf{MAE} or \textbf{mean absolute error} is similar to RMSE, but penalises outliers less. It is computed using the average of the absolute errors: $MAE = \frac{\sum\left|predicted-actual\right|}{n}$
	\item The \textbf{Pearson correlation coefficient}, a popular measure for continuous data, is a number between -1 and 1 that quantifies the correlation between two variables, each having a separate value set. We can interpret this as how much the variable movement through its value set corresponds to the movement of the other variable in its own value set. Values close to 1 mean that greater values of the one variable imply greater values for the second variable, negative values mean the two variables move in opposite directions, and values close to 0 mean there is no correlation between the two variables. However, one must keep in mind that correlation does not imply causality, so the presence of correlation between two variables does not mean that one of them has any influence on the other one. If we compare red Ferrari cars to blue Renault cars, one may find a correlation between car color red and car speed. However, this does not imply that red cars are faster.
\end{enumerate}

\section{Tools}
We used \textbf{Weka} 3.8 for building and training the model trees for the phoneme duration prediction. It is an open source freeware using a Java VM, and contains a collection of tools for all machine learning tasks we needed, from data pre-processing over classification and regression till model evaluation and data visualization.

In order to extract the needed information from our database, and put it in a form ready to use with Weka, we used self-made code written in Python 3.6. This is an easy to learn programming language with many features dedicated to statistical analysis and even machine learning. Most of the figures in this paper were produced in python as well.
